Prediction of the 2020 Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
idk
bunch of updates
push

# post-stratified estimates - number of trump votes
estimate_votes <- cell_counts %>% mutate(predict_prop = proportion * estimate) %>% group_by(state_name) %>% summarise(pred_vote = sum(predict_prop))
estimate_votes

>>>>

# post-stratified estimates - number of trump votes
estimate_votes <- cell_counts %>% mutate(predict_prop = proportion * estimate) %>% group_by(state_name) %>% summarise(pred_vote = sum(predict_prop),
                                                                                                                      mean_vote = mean(predict_prop))
estimate_votes

cell_counts
